The \dealii{} Library, Version 8.4.0

### 2016-02-28 deal84.tex
add a section on shared tria

\title{The \dealii{} Library, Version 8.4.0}
\author[1]{Wolfgang Bangerth}
\affil[1]{Department of Mathematics, Texas A\&M University, College Station,
    TX 77843, USA,
    {\texttt{bangerth@math.tamu.edu}}}
\author[2]{Denis Davydov}
\affil[2]{???,
  {\texttt{???}}}
\author[3]{Timo Heister}
\affil[3]{Mathematical Sciences,
  O-110 Martin Hall.
  Clemson University.
  Clemson, SC 29634, USA,
  {\texttt{heister@clemson.edu}}}
\author[4]{Luca Heltai}
\affil[4]{SISSA - International School for Advanced Studies, Via
  Bonomea 265, 34136 Trieste, Italy,
  {\texttt{luca.heltai@sissa.it}}}
\author[5]{Guido Kanschat}
\affil[5]{Interdisciplinary Center for Scientific Computing (IWR),
  Universit{\"a}t Heidelberg, Im Neuenheimer Feld 368, 69120 Heidelberg, Germany,
  {\texttt{kanschat@uni-heidelberg.de}}}
\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics, Technische
  Universit{\"a}t M{\"u}nchen, Boltzmannstr.~15, 85748 Garching b. Mænchen,
  Germany,
  {\texttt{kronbichler@lnm.mw.tum.de}}}
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics, University of Minnesota, 127 Vincent Hall,
  206 Church Street SE, Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}
\author[8]{Bruno Turcksin}
\affil[8]{Department of Mathematics, Texas A\&M University, College Station,
  TX 77843, USA,
  {\texttt{turcksin@math.tamu.edu}}}
\author[9]{David Wells}
\affil[9]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}
%\author[8]{Toby~D.~Young}
%\affil[8]{Institute of Fundamental Technological Research of the Polish
%  Academy of Sciences, ul. Pawi{\'n}skiego 5b, Warsaw 02-106, Poland,
%  {\texttt{tyoung@ippt.pan.pl}}}

@@

\marginpar{Denis -- can you write this section?}
...

>>>>

\title{The \dealii{} Library, Version 8.4.0}
\author[1]{Wolfgang Bangerth}
\affil[1]{Department of Mathematics, Texas A\&M University, College Station,
    TX 77843, USA,
    {\texttt{bangerth@math.tamu.edu}}}
\author[2]{Denis Davydov}
\affil[2]{Chair of Applied Mechanics, University of
    Erlangen-Nuremberg, Egerlandstr. 5, 91058 Erlangen, Germany,
  {\texttt{denis.davydov@fau.de}}}
\author[3]{Timo Heister}
\affil[3]{Mathematical Sciences,
  O-110 Martin Hall.
  Clemson University.
  Clemson, SC 29634, USA,
  {\texttt{heister@clemson.edu}}}
\author[4]{Luca Heltai}
\affil[4]{SISSA - International School for Advanced Studies, Via
  Bonomea 265, 34136 Trieste, Italy,
  {\texttt{luca.heltai@sissa.it}}}
\author[5]{Guido Kanschat}
\affil[5]{Interdisciplinary Center for Scientific Computing (IWR),
  Universit{\"a}t Heidelberg, Im Neuenheimer Feld 368, 69120 Heidelberg, Germany,
  {\texttt{kanschat@uni-heidelberg.de}}}
\author[6]{Martin Kronbichler}
\affil[6]{Institute for Computational Mechanics, Technische
  Universit{\"a}t M{\"u}nchen, Boltzmannstr.~15, 85748 Garching b. Mænchen,
  Germany,
  {\texttt{kronbichler@lnm.mw.tum.de}}}
\author[7]{Matthias Maier}
\affil[7]{School of Mathematics, University of Minnesota, 127 Vincent Hall,
  206 Church Street SE, Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}
\author[8]{Bruno Turcksin}
\affil[8]{Department of Mathematics, Texas A\&M University, College Station,
  TX 77843, USA,
  {\texttt{turcksin@math.tamu.edu}}}
\author[9]{David Wells}
\affil[9]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA
  {\texttt{wellsd2@rpi.edu}}}
%\author[8]{Toby~D.~Young}
%\affil[8]{Institute of Fundamental Technological Research of the Polish
%  Academy of Sciences, ul. Pawi{\'n}skiego 5b, Warsaw 02-106, Poland,
%  {\texttt{tyoung@ippt.pan.pl}}}

@@

Previously, in order to use \texttt{Triangulation<dim,spacedim>} class with MPI one had to manually
partition triangulation (e.g. via \texttt{METIS}), calculate and store index sets of locally owned and locally relevant degrees-of-freedom (DoF), querry \texttt{subdomain\_id}  of a cell during assembly etc.
In order to facilitate the usage of \texttt{Triangulation} class with MPI  
and to make its behaviour in this context consistent with \texttt{parallel::distributed::Triangulation}, a new class
\texttt{parallel::shared::Triangulation} was introduced. 
It extends \texttt{Triangulation} class to automatically partition triangulation when run with MPI.
Identical functionality between \texttt{shared} and \texttt{distributed} triangulation  
(e.g. locally owned and relevant DoFs, mpi communicator, etc)
is grouped in the parent class \texttt{parallel::Triangulation}.
The main difference between the two parallel triangulations is that in the case of 
\texttt{parallel::shared::Triangulation} each process stores all cells of the triangulation.
Consequently, by default there are no artificial cells. 
That is, cells which are attributed to the current processor are marked as locally owned 
(\texttt{cell->is\_locally\_owned()} returns \texttt{true}) 
and the rest are ghost cells.
This behaviour can be altered via an additional boolean flag provided to the constructor of the class. 
In this case, a set of ghost cells will consist of a halo layer of cells around locally owned cells.
Cells which are neither ghost nor locally owned are marked as artificial.
This is consistent with the behaviour of \texttt{parallel::distributed::Triangulation},
although in the latter case the size of the set of artificial cells will be much smaller.
The introduction of \texttt{parallel::shared::Triangulation} class together with the 
optional artificial cells and parent \texttt{parallel::Triangulation} class
facilitates writing
algorithms that are indifferent to the way triangulation is stored in the MPI context. 
For example, \texttt{DoFTools::locally\_relevant\_dofs()} will now return a subset of 
all DoFs for both triangulations, granted that artificial cells are enabled in 
\texttt{parallel::shared::Triangulation}.
Assmebly routines can now use \texttt{cell->is\_locally\_owned()} 
for both triangulations.
Currently, only standard (non hp) \texttt{DoFHandler} is supported.
